Tropical Andes plant Lookup Table

### 2023-09-27 code/L1/L1_TropicalAndes_plant_lookupTable.Rmd
update file path, gbif species list spilt; add code to subset results

# Set file paths
```{r}
data_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
```

@@

# Read in species lists
```{r}
TRY_species <- read.csv(file.path(data_path,"TropicalAndes_TRY_plant_species.csv"))
BIEN_species <- read.csv(file.path(data_path,"TropicalAndes_BIEN_plant_trait_species.csv"))
GBIF_species <- read.csv(file.path(data_path,"TropicalAndes_GBIF_plant_species.csv"))
```

```{r}
# convert species list to character
TRY_species_chr <- as.character(TRY_species$x)
BIEN_species_chr <- as.character(BIEN_species$x)
GBIF_species_chr <- as.character(GBIF_species$x)
```

# Using TNRS
```{r}
BIEN_results <- TNRS(taxonomic_names = BIEN_species)
TRY_results <- TNRS(taxonomic_names = TRY_species)
GBIF_results <- TNRS(taxonomic_names = GBIF_species)
```

# Using taxsize
```{r}
GBIF_species_resolved <- resolve(GBIF_species)
TRY_species_resolved <- resolve(TRY_species)
BIEN_species_resolved <- resolve(BIEN_species)
```

>>>>

# Set file paths
```{r}
data_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
data_path2 <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
output_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
```

@@

# Read in species lists
```{r}
TRY_species <- read.csv(file.path(data_path,"TropicalAndes_TRY_plant_species.csv"))
BIEN_species <- read.csv(file.path(data_path,"TropicalAndes_BIEN_plant_trait_species.csv"))
GBIF_species <- read.csv(file.path(data_path2,"TropicalAndes_plant_Forest_SpeciesList.csv"))
```

# Using TNRS
```{r}
BIEN_results <- TNRS(taxonomic_names = BIEN_species)
```

```{r}
TRY_results <- TNRS(taxonomic_names = TRY_species)
```

```{r}
#split up gbif species list to speed up api call
GBIF_species1 <-GBIF_species[1:2245,]
GBIF_species2 <-GBIF_species[2245:6745,]
GBIF_species3 <-GBIF_species[6745:11245,]
GBIF_species4 <-GBIF_species[11245:15745,]
GBIF_species5 <-GBIF_species[15745:20245,]
GBIF_species6 <-GBIF_species[16553:20245,]
GBIF_species7 <-GBIF_species[20245:24745,]
GBIF_species8 <-GBIF_species[24745:29245,]
GBIF_species9 <-GBIF_species[29245:33745,]
GBIF_species10 <-GBIF_species[33745:38245,]
GBIF_species11 <-GBIF_species[38245:42745,]
GBIF_species12 <-GBIF_species[42745:47245,]
```

```{r}
GBIF_results1 <- TNRS(taxonomic_names = GBIF_species1)
GBIF_results2 <- TNRS(taxonomic_names = GBIF_species2)
GBIF_results3 <- TNRS(taxonomic_names = GBIF_species3)
GBIF_results4 <- TNRS(taxonomic_names = GBIF_species4)
GBIF_results5 <- TNRS(taxonomic_names = GBIF_species5)
GBIF_results6 <- TNRS(taxonomic_names = GBIF_species6)
GBIF_results7 <- TNRS(taxonomic_names = GBIF_species7)
GBIF_results8 <- TNRS(taxonomic_names = GBIF_species8)
GBIF_results9 <- TNRS(taxonomic_names = GBIF_species9)
GBIF_results10 <- TNRS(taxonomic_names = GBIF_species10)
GBIF_results11 <- TNRS(taxonomic_names = GBIF_species11)
GBIF_results12 <- TNRS(taxonomic_names = GBIF_species12)
```

```{r}
#combine gbif results
GBIF_results <- rbind(GBIF_results1, GBIF_results2, GBIF_results3, GBIF_results4, GBIF_results5, GBIF_results6, GBIF_results7, GBIF_results8, GBIF_results9, GBIF_results10, GBIF_results11, GBIF_results12)
```

# Save full results
```{r}
write.csv(BIEN_results, file.path(output_path,"BIEN_plant_species_resolved_output_full.csv"))
write.csv(TRY_results, file.path(output_path,"TRY_plant_species_resolved_output_full.csv"))
write.csv(GBIF_results, file.path(output_path,"GBIF_plant_species_resolved_output_full.csv"))
```

# Subset results to species with matches, conflicts, and disparties
Name_submitted values not the same as Accepted_name
```{r}
BIEN_matches <- subset(BIEN_results, Taxonomic_status == "Accepted")
#Results in 3799 species
BIEN_conflicts <- subset(BIEN_results, Taxonomic_status == "Synonym")
#Results in 646 species
BIEN_disparities <- subset(BIEN_results, Taxonomic_status %in% c("No opinion", "Illegitimate", "Invalid", ""))
#Results in 44 species
```

```{r}
TRY_matches <- subset(TRY_results, Taxonomic_status == "Accepted")
#Results in 4043 species
TRY_conflicts <- subset(TRY_results, Taxonomic_status == "Synonym")
#Results in 307 species
TRY_disparities <- subset(TRY_results, Taxonomic_status %in% c("No opinion", "Illegitimate", "Invalid", ""))
#Results in 37 species
```

```{r}
GBIF_matches <- subset(GBIF_results, Taxonomic_status == "Accepted")
#Results in 47554 species
GBIF_conflicts <- subset(GBIF_results, Taxonomic_status == "Synonym")
#Results in 1572 species
GBIF_disparities <- subset(GBIF_results, Taxonomic_status %in% c("No opinion", "Illegitimate", "Invalid", ""))
#Results in 1821 species
```

# Checking 
```{r}

```
